\section{Related Work}
\label{sec:related_work}

Most self-supervised methods for images learn representations by making the
embeddings of two augmented views of the same image agree, while avoiding the
trivial solution in which every image maps to the same embedding (complete
collapse). Contrastive methods such as SimCLR~\cite{chen2020simclr} and
MoCo-v3~\cite{chen2021mocov3} prevent collapse by also pushing apart
embeddings of different images. Self-distillation methods such as
BYOL~\cite{grill2020byol} and DINO~\cite{caron2021dino} prevent it with
asymmetry between two networks, and masked autoencoders~\cite{he2022mae}
avoid view agreement altogether by reconstructing masked input patches.
Barlow Twins~\cite{zbontar2021barlow} instead pushes the cross-correlation
matrix between the two views' embeddings toward the identity matrix: the
diagonal enforces view invariance, the off-diagonal decorrelates embedding
dimensions, and the objective itself penalizes collapse with neither negative
pairs nor network asymmetry. We adopt the Barlow Twins objective and its
reference loss implementation unchanged, adapt the recipe to $64\times64$
inputs and small-batch ViT training (Section~\ref{sec:method}), and
characterize how the method behaves as pre-training data shrinks.

How much pre-training data self-supervised learning needs is a well-studied
question. Contrastive learning has been measured across data quantity,
domain, and quality, with modest benefit from pre-training data beyond 500k
images~\cite{cole2022when}. Closer to our scale, denoising autoencoders
(BEiT-style masked prediction) have been reported more robust to the size and
type of the pre-training set than joint-embedding methods, represented there
by DINO and evaluated by fine-tuning; under linear probing, the same study
reports denoising autoencoders falling
behind~\cite{elnouby2021largescale}. At the opposite end of the scale,
joint-embedding training on a large enough dataset needs almost no
augmentations beyond cropping: hand-crafted augmentations act chiefly by
artificially enlarging the dataset, so their benefit concentrates where data
is limited~\cite{moutakanni2024you} --- though the smallest scale tested
there is 1.3M images, far above ours. These studies chart the small-data
regime across method families, but none of them measures Barlow Twins. So we
characterize the data efficiency of Barlow Twins directly, on a small ViT,
from 1k to 100k pre-training images, under a linear-probe evaluation.

Comparing models pre-trained on different set sizes requires a schedule that
does not tie model quality to a pre-committed stopping point, and cosine
learning-rate schedules~\cite{loshchilov2017sgdr} do exactly that: a
checkpoint read out well before the cosine horizon attains higher loss than a
model whose schedule was matched to that
duration~\cite{hoffmann2022chinchilla}. Warmup-stable-decay (WSD) schedules
avoid the committed horizon and match the final loss of a well-tuned
cosine~\cite{hagele2024scaling,hu2024minicpm}; horizon-free schedules of this
family have precedent in vision-transformer
scaling~\cite{zhai2022scalingvit} and continual
pre-training~\cite{singh2025beyond}. So we train every set size with a
WSD-style schedule, assembled from these published components
(Section~\ref{sec:method}); the schedule is not a contribution of this work.

Self-supervised training also needs a validation signal for checkpoint
selection. The standard monitor is $k$-nearest-neighbor classification on
frozen features over held-out in-domain data, as in DINO with
$k{=}20$~\cite{caron2021dino}; fully label-free alternatives based on
embedding rank exist~\cite{garrido2023rankme}, which we log but do not select
with. So we follow the $k$NN convention, smoothed against selection
bias~\cite{cawley2010overfitting} as Section~\ref{sec:method} details.

A representation can also degrade without collapsing completely: in
dimensional collapse, the embedding variance concentrates in a
low-dimensional subspace~\cite{jing2022dimensional}, which the effective rank
of the feature covariance spectrum quantifies~\cite{roy2007effective}.
Augmentations are not a free remedy in this regime. The invariances a
joint-embedding method learns are the invariances its augmentations
define~\cite{xiao2021what}, and views that share too little information
destroy task-relevant signal~\cite{tian2020infomin}; for supervised ViTs,
augmentation and regularization can substitute for an order of magnitude of
training data~\cite{steiner2022train}, underlining how strongly augmentation
choices act as implicit data. So in the small-data regime we keep the
augmentation recipe fixed --- the published one, adapted once to
$64\times64$ inputs (Section~\ref{sec:method}) --- and track effective rank
as a logged collapse diagnostic.
